---
title: "ENV H 570: Lab 3"
author: Joan A. Casey, with updates from Lauren B. Wilner and Brian High
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
        df_print: paged
        theme: cosmo
        toc: yes
---

## Objective
The objective of this lab is to run a synthetic control model. We will leverage Dr. Brooke Anderson’s `hurricaneexposure` package and estimate the impact of hurricane exposure on mortality.

## Setup
```{r setup, include = TRUE, warning=FALSE, results='hide', message=FALSE}
# Clear workspace of all objects and unload all extra (non-base) packages.
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

# Load packages, installing if needed
if(!requireNamespace("pacman", quietly = TRUE)){
  install.packages("pacman")}
pacman::p_load(
  conflicted, 
  here,
  weathermetrics,
  dplyr,
  tidyr,
  sf,
  ggplot2,
  MetBrewer,
  BiocManager,
  LowRankQP,
  Synth,
  drat # need this package to do the special install below
)

# Load packages that have to be pulled directly from github
# We will install and load the tidysynth & hurricaneexposure packages and dependencies
# also need to load hurricaneexposuredata in a specific way
pacman::p_load_gh("edunford/tidysynth")
pacman::p_load_gh("geanders/hurricaneexposure")
addRepo("geanders")
pacman::p_load("hurricaneexposuredata")

# Let's use conflict prefer again to make sure that we use these functions
# from the right package. We'll leave the instances of `hurricaneexposure::` 
# since this package is new to you and we want you to see which functions come 
# from it.
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::left_join)

```

## Load and clean data 
### Hurricane data
```{r hurr_data, echo=TRUE, warning=FALSE, message=FALSE}
data("hurr_tracks")
glimpse(hurr_tracks)

# Visualize hurricane data 
# Storm track
hurricaneexposure::map_tracks(storm = "Florence-2018")
# Distance from the storm track to the county
hurricaneexposure::map_counties(storm = "Florence-2018", metric = "distance")
# Estimated wind speed in the county
hurricaneexposure::map_counties(storm = "Florence-2018", metric = "wind")
# Estimated wind gusts in the county
hurricaneexposure::map_counties(storm = "Florence-2018", metric = "wind", 
                                wind_var = "vmax_gust")

# Distance from Hurricane
dist <- hurricaneexposure::filter_storm_data(
  storm = "Florence-2018", output_vars = c("fips", "closest_date", "storm_dist"))
dist <- dist %>% mutate(closest_date = as.Date(closest_date))
```

Let's consider Onslow, NC as our exposed county. The FIPS code is 37133. Let's also consider counties that are more than 200km from the storm as unexposed. Accordingly, we can subset our data to our one exposed county (Onslow) and our unexposed counties, from which we will construct our synthetic control. 

```{r hurr_data2, echo=TRUE, warning=FALSE, message=FALSE}
# Identifying counties located farther than 200 km (unexposed group)
dist <- dist %>% filter(fips=="37133" | storm_dist>200)

# Create binary exposed variable 
dist <- dist %>% mutate(exposed = ifelse(fips=="37133", 1,0))

# Check data
table(dist$exposed) # 1 exposed county (Onslow)
```

### All-cause mortality data
Now let's bring in our outcome data. We'll restrict to counties that are in our exposure data, as we don't need outcome data for counties that do not have exposure data. Hurricane Florence occurred in 2018, so we'll also filter to 2000-2018 since we don't want years after our exposure included. Finally, let's create a state fips code and a rate metric for our modeling step! 
```{r mort, echo=TRUE, warning=FALSE, message=FALSE}
mortality <- readRDS(here("data/lab/03/county_mortality.RDS"))

# Restrict to counties in dist dataframe
mortality <- mortality %>% filter(fips %in% dist$fips)

# Filter to before 2018 and after 1999
mortality <- mortality %>% filter(year>1999 & year<2019) 

# # Filter to September (month of hurricane exposure in 2018)
mortality <- mortality %>% filter(month==9) 

# Create state fips
mortality  <-  mortality %>% mutate(st_fips = substr(fips, 1, 2))

# Create a variable that is the death rate per 1,000
mortality <- mortality %>% mutate(death_rate = n_deaths/pop * 1000)
```

### Covariate data
Lastly, we will bring in our covariate data. For this analysis, we will use annual median income and unemployment data. 
```{r cov, echo=TRUE, warning=FALSE, message=FALSE}
covar <- readRDS(here("data/lab/03/income_unemp.rds"))
```

### Compile modeling dataset
```{r compile, echo=TRUE, warning=FALSE, message=FALSE}
df_temp <- left_join(mortality, covar)
df <- left_join(df_temp, dist)
head(df)
```

## Synthetic control model
Now we are ready to build our modeling dataset! Let's drop missing observations, restrict to only a few states for our eligible control counties (to make sure our run time is reasonable) and make sure we only have counties with a full time series of data (all years).
```{r mod_prep, echo=TRUE, warning=FALSE, message=FALSE}
# Get rid of missing data because we need complete dataset for this code to work
summary(df)
df <- df %>% tidyr::drop_na(death_rate, unemp, med_inc)

# Look at the number of counties by state
table(df$state_name)

#Confirm exposed county in the dataframe
df %>% filter(exposed==1) 

# Also going to restrict to counties in Georgia, Maryland, Virginia
# because model takes too long to run
df <- df %>% filter(
  state_name == "Georgia" |
    state_name == "Maryland" |
    state_name == "Virginia" |
    fips=="37133" ) #Need to keep county of interest that is outside of TX, MO, NC

# Just keep needed variables
df <- df %>% select(fips, year, death_rate, unemp, med_inc)

# Also need counties to have complete years
df <- df %>% group_by(fips) %>% mutate(n=n())
table(df$n)
table(df$year)
df <- df %>% filter(n==18) # just keeping counties with data in all 18 years
```

### Run synthetic control
Now we can run our model! This may take about 10-15 minutes, so make sure you stay connected to the internet and your R session.
```{r mod, echo=TRUE, warning=FALSE, message=FALSE}
model <-
  df %>%
  # initial the synthetic control object
  synthetic_control(
    outcome = death_rate,
    # outcome
    unit = fips,
    # unit index in the panel data
    time = year,
    # time index in the panel data
    i_unit = "37133",
    # unit where the intervention occurred
    i_time = 2018,
    # time period when the intervention occurred
    generate_placebos = T # generate placebo synthetic controls (for inference)
  ) %>%

  # Generate the aggregate predictors used to fit the weights
  generate_predictor(
    time_window = 2000:2018,
    mmed_inc = mean(med_inc, na.rm = T),
    muemply = mean(unemp, na.rm = T)
  ) %>%

  # Lagged mortality
  generate_predictor(time_window = 2000,
                     death_2000 = death_rate) %>%
  generate_predictor(time_window = 2001,
                     death_2001 = death_rate) %>%
  generate_predictor(time_window = 2002,
                     death_2002 = death_rate) %>%
  generate_predictor(time_window = 2003,
                     death_2003 = death_rate) %>%
  generate_predictor(time_window = 2004,
                     death_2004 = death_rate) %>%
  generate_predictor(time_window = 2005,
                     death_2005 = death_rate) %>%
  generate_predictor(time_window = 2006,
                     death_2006 = death_rate) %>%
  generate_predictor(time_window = 2007,
                     death_2007 = death_rate) %>%
  generate_predictor(time_window = 2008,
                     death_2008 = death_rate) %>%
  generate_predictor(time_window = 2009,
                     death_2009 = death_rate) %>%
  generate_predictor(time_window = 2010,
                     death_2010 = death_rate) %>%
  generate_predictor(time_window = 2011,
                     death_2011 = death_rate) %>%
  generate_predictor(time_window = 2012,
                     death_2012 = death_rate) %>%
  generate_predictor(time_window = 2013,
                     death_2013 = death_rate) %>%
  generate_predictor(time_window = 2014,
                     death_2014 = death_rate) %>%
  generate_predictor(time_window = 2015,
                     death_2015 = death_rate) %>%
  generate_predictor(time_window = 2016,
                     death_2016 = death_rate) %>%
  generate_predictor(time_window = 2017,
                     death_2017 = death_rate) %>%


  # Generate the fitted weights for the synthetic control
  generate_weights(optimization_window = 2000:2018,
                   margin_ipop = .02, sigf_ipop = 7, bound_ipop = 6) %>% # time to use in the optimization task

  # Generate the synthetic control
  generate_control()
```

If this code runs too slowly and never finishes, you can also read in the model results from the rds file on Canvas. You can comment out or delete the model above and instead pull in model results that we ran and saved. You will need to download the file and upload it to the server using the upload button under `Files`. Make sure you read it from the filepath where you upload it! 

```{r alt_mod, echo=TRUE, warning=FALSE, message=FALSE}
# model <- readRDS("~/synth_control_results.rds")
```

## Plotting and model diagnostics
Let's take a look at our model.
```{r plot, echo=TRUE, warning=FALSE, message=FALSE}
# Plot Onslow County over time versus other counties included
model %>% plot_trends()

# Plot differences in counties over time
model %>% plot_differences()

# How balanced were we after implementing the synthetic control?
model %>% grab_balance_table()

# Which of our (limited) variables contributed most?
model %>% plot_weights()

# Which counties contribute most to the synthetic control?
weights <- model %>% grab_unit_weights()
weights
```


