---
title: "ENV H 570: Lab 4"
author: Joan A. Casey
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
        df_print: paged
        theme: cosmo
        toc: yes
---

## Objective
The goal of this lab is to work with various spatial data sources and explore different ways to map and visualize them. We will work with some data from Seattle on SES, income, and housing vacancy, in addition to noise data from two different sources -- the data that we collected as a class and data from a national noise model. We will explore different ways of combining and displaying thes data.

## Setup
```{r setup, include = TRUE, warning=FALSE, results='hide', message=FALSE}
# Clear workspace of all objects and unload all extra (non-base) packages.
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

# Load packages, installing if needed
if (!requireNamespace("pacman", quietly = TRUE)){
  install.packages("pacman")}
pacman::p_load(
  conflicted, 
  here,
  dplyr,
  tidyr, 
  sf,
  ggplot2,
  MetBrewer,
  RColorBrewer,
  patchwork,
  readr,
  leaflet,
  leaflegend,
  ggmap,
  raster
)
```

## Load and clean data 
### Seattle SES and tree coverage data
What projection are these data in? Let's also visualize them to get a sense of what is there!
```{r sea_data, echo=TRUE, warning=FALSE, message=FALSE}
seattle <- st_read(here("data/lab/04/seattle_tree_ses_ct.shp"))
dplyr::glimpse(seattle)

# Plot tree density
tree_density <- ggplot() +
  geom_sf(data = seattle, aes(fill = tr_dnst)) +
  theme_void(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  scale_fill_gradientn("Tree density \n(per mi2)",
                       colors = met.brewer("VanGogh3"),
                       na.value = "grey50")


# Plot median income
income <- ggplot() +
  geom_sf(data = seattle, aes(fill = MEDIAN_)) +
  theme_void(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) + scale_fill_gradientn("Median income ($)",
                           colors = met.brewer("Degas"),
                           na.value = "grey50")

#Plotting these side-by-side using patchwork
tree_density + income

# Try adding figure for percent vacant housing below
vacant <- ggplot() +
  geom_sf(data = seattle, aes(fill = PCT_VAC)) +
  theme_void(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) + scale_fill_gradientn("% vacant",
                           colors = met.brewer("Degas"), 
                           na.value = "grey50")

#Plotting these side-by-side using patchwork
tree_density + income + vacant
```

Do you notice any issues with the color palette here? Let's try again with a better color palette for percent vacant homes.

```{r sea_data2, echo=TRUE, warning=FALSE, message=FALSE}
flipped_palette <- rev(met.brewer("Degas"))
vacant <- ggplot() +
  geom_sf(data = seattle, aes(fill = PCT_VAC)) +
  theme_void(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) + scale_fill_gradientn("% vacant",
                           colors = flipped_palette, 
                           na.value = "grey50")
tree_density + income + vacant 
```

### Crowd-sourced noise measurements
Let's now load and clean our crowd-sourced noise measurements. Cool that R recognizes the time column as time of day.
```{r noise_dat, echo=TRUE, warning=FALSE, message=FALSE}
noise <-
  read_csv(here("data/lab/04/noise_envh570_seattle_2024.csv")) 

#glimpse it
glimpse(noise)

# Remove erroneous rows of data
noise <- drop_na(noise)

# how does these data look? see any problems?
summary(noise)

#correct an error in data entry (someone missed a -)
noise <- noise %>% mutate(longit = ifelse(longit<0, longit, -1*longit))

# make an sf object with lat/longit
noise_sf <-
  st_as_sf(noise, coords = c("longit", "latit"), crs = "EPSG:4326")

# get coordinates
coords <- st_coordinates(noise_sf)
lat = coords[, 2]
long = coords[, 1]
```

Now we can make a map of our noise data in Seattle. You can change long/lat/zoom as you see fit. 
```{r noise_dat2, echo=TRUE, warning=FALSE, message=FALSE}
m <- leaflet() %>% setView(lng = -122.34,
                           lat = 47.65,
                           zoom = 12)

m <- m %>% addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers(
    m,
    lng = long,
    lat = lat,
    popup = m$noise,
    label = m$noise
  )
m
```

We can also make a map with symbols proportional to the noise level, rather than uniform markers. 

```{r noise_dat3, echo=TRUE, warning=FALSE, message=FALSE}
# Let's make a proportional symbol map
symbols <- makeSymbolsSize(
  values = noise_sf$noise,
  shape = 'circle',
  color = 'blue',
  fillColor = 'blue',
  opacity = .5,
  baseSize = 10
)

# Making the map
m2 <- leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers(
    data = m,
    icon = symbols,
    lng = long,
    lat = lat
    ) %>%
  addLegendSize(
    values = noise_sf$noise,
    color = 'blue',
    fillColor = 'blue',
    opacity = .5,
    title = 'Leq noise (dBA)',
    shape = 'circle',
    orientation = 'horizontal',
    breaks = 5)
m2
```

## Noise and social environment
Now that we have loaded, cleaned, and visualized our data, let's combine our crowd sourced noise data with the data on the social environment in Seattle. We first need to make sure everything we combine is in the same CRS, and then we can map them together.
```{r noise_soc, echo=TRUE, warning=FALSE, message=FALSE}

# Change noise measurements into same projection as Seattle shapefile
noise_sf <- st_transform(noise_sf, crs = st_crs(seattle))

# Map points on the tree map
ggplot() +
  geom_sf(data = seattle, aes(fill = tr_dnst)) +
  geom_sf(data = noise_sf, aes(size=noise), color="grey", alpha=0.5) +
  theme_void(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  scale_fill_gradientn("Tree density \n(per mi2)",
                       colors = met.brewer("VanGogh3"),
                       na.value = "grey50") +
  scale_size_continuous("Noise level (dB)")
```

Now create a similar map with income. 
```{r noise_soc2, echo=TRUE, warning=FALSE, message=FALSE}
## ADD HERE ##
```

## Crowd-sourced noise vs. national noise model 
Let's take a look at how our crowd-sourced noise compares to a national noise model! 

### Load and examine
```{r noise_noise, echo=TRUE, warning=FALSE, message=FALSE}
transit_noise <- terra::rast(here("data/lab/04/seattle_transit.tif"))

# Check out specs of the raster data
transit_noise
```
How many columnns and rows of data? How many total grid cells?

### Plot
```{r noise_noise2, echo=TRUE, warning=FALSE, message=FALSE}
# Plot it
plot(transit_noise)
```

### Match up to crowd-sourced noise
```{r noise_noise3, echo=TRUE, warning=FALSE, message=FALSE}
# Extract transit noise levels where we took noise measurements
noise_from_transit_model <- terra::extract(transit_noise, noise_sf)

# Gives us values from from the transit noise raster
# We need to add them back to the noise_sf shapefile
noise_sf <- noise_sf %>% mutate(transit_noise = noise_from_transit_model)
```

### Correlation between noise sources
What is the correlation between our measurements and the model? We can look at this visually and also can look at a correlation coefficient. Add a Pearson correlation coefficient to the end here. How correlated are our data? 
```{r noise_noise4, echo=TRUE, warning=FALSE, message=FALSE}
ggplot(noise_sf, aes(x=noise, y=transit_noise$seattle_transit)) + geom_point() + 
  geom_smooth() +
  theme_minimal() +
  geom_abline(linetype="dashed") + # adding a reference line +
  scale_x_continuous("Our noise measurements (dBA)", limits=c(40,80))+
  scale_y_continuous("Transit noise model (dBA)", limits=c(40,80))

# Pearson and Spearman correlation
cor.test(noise_sf$noise, noise_sf$transit_noise$seattle_transit,
         method = "spearman")

# You do Pearson 
# ADD HERE
```



