---
title: "ENV H 570: Lab 1"
author: Joan A. Casey
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
        df_print: paged
        theme: cosmo
        toc: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "build") })
---

## Objective
This file is meant to get you acclimated to the online RStudio environment and introduce you to basic commands to explore data. We will use fetal death data and we will examine the data in R, manipulate the data to create meaningful plots, and finally map the data. The last part of this lab contains an optional series of steps to create cartograms and run a simple regression model. 

## Setup
```{r setup, include = TRUE, warning=FALSE, results='hide', message=FALSE}
# Clear workspace of all objects and unload all extra (non-base) packages.
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

# Load packages, installing if needed
if (!requireNamespace("pacman", quietly = TRUE)){ 
  install.packages("pacman")
  }

pacman::p_load(
  conflicted, 
  here,
  usethis,
  Hmisc,
  dplyr,
  readr,
  tidyr,
  explore,
  rlang,
  ggplot2,
  RColorBrewer,
  tmap,
  sf,
  viridis,
  corrr,
  marginaleffects,
  spdep,
  cartogram
)

# Declare a package preference for filter() with `conflicts_prefer()`:
# this is needed because other packages have functions called `filter`
# and we want to make sure we are using dplyr's `filter` function. 
# the other way to do this is to type `dplyer::filter` every time we want to 
# use filter.
conflicts_prefer(dplyr::filter)
conflicts_prefer(tidyr::expand)
conflicts_prefer(corrr::correlate)
conflicts_prefer(dplyr::select)

```

## Part 1: Fetal death (outcome) data cleaning
### I. Read in and explore outcome data 
```{r fetal_deaths, echo=TRUE, warning=FALSE}
# Read in outcome data (fetal deaths = "spontaneous intrauterine death of a 
# fetus at any time during pregnancy"), downloaded from CDC Wonder:
# https://wonder.cdc.gov/fetal-deaths-current.html
fetal_data <- read_csv(here("data/lab/01/fetal_death.csv"))

# Explore the data using dplyr::glimpse
glimpse(fetal_data)

# Explore the data using summary
summary(fetal_data)

# Explore the data using explore::describe_tbl and explore::describe
explore::describe_tbl(fetal_data)
explore::describe(fetal_data)

# Explore the data using Hmisc::describe
Hmisc::describe(fetal_data)

# How many states are included in the dataset? Find out using n_distinct. Which 
# package has the n_distinct command?
n_distinct(fetal_data$state) # 50 states + DC

```
### II. Manipulate outcome data to handle missingness 
```{r outcome_missingness, echo=TRUE, warning=FALSE}
# Some states do not have data for each year/race/death combo
# If table shows two entries for a state, they have counts for both Black and 
# white pregnant people
table(fetal_data$state, fetal_data$year)

# Expand so we have a row for each year/race/state combo
# We expect a dataframe 51 states x 4 years x 2 race/ethnicities = 408
# This dataframe does not contain the fetal_deaths but is just a square template
# that we can use to create a dataset that has every state/yr/raceeth combo 
# regardless of whether there were fetal deaths or not. 
fetal_data_expanded <- fetal_data %>% expand(state, year, mom_race_eth)
dim(fetal_data_expanded)
head(fetal_data_expanded)

# Now we can merge our fetal deaths (`fetal_data`) onto our template
# `fetal_data_new` so we have a row for every state/yr/raceeth combo. We can use 
# left join so that we keep all rows from `fetal_data_new` and rows where we
# don't have fetal death data (due to small numbers) will have NAs. 
# Please read about left_join by typing ?left_join into the console
fetal_data_new <- left_join(
  fetal_data_expanded,
  fetal_data,
  by = c(
    "state" = "state",
    "year" = "year",
    "mom_race_eth" = "mom_race_eth"
  )
)

# Glimpse it
glimpse(fetal_data_new)

```

### III. Plot outcome data 
Let's create a visualization of fetal death counts by race/ethnicity in 2017. 

A few things we want to do for aesthetics of our plot:   

1. We want to order our y-axis by total fetal deaths for a given state-year to make it easier to read.  
2. Our race/ethnicity labels are long right now, so let's make a variable with shorter names   
3. Filter to the year 2017   
4. Plot!   


```{r plot_outcome, echo=TRUE, warning=FALSE}
# 1. To do this, first we will create a total fetal deaths variable which will
# reflect the total fetal deaths by state-year. So,to do this, we `group_by` 
# state and year and then use `mutate` to create a new variable that is the sum
# of `fetal_deaths` by those grouping vars (state, year)
fetal_data_new <- fetal_data_new %>% group_by(state, year) %>% 
  mutate(total_fetal_deaths=sum(fetal_deaths, na.rm=T))

# 2. Let's make a new variable for plotting purposes that has shorter labels. 
# We can create a new variable called "mom_race_eth_plot" that replaces "Black or 
# African American" with "Black" for simplicity
fetal_data_new <- fetal_data_new %>%
  mutate(mom_race_eth_plot = ifelse(
    mom_race_eth == "Black or African American",
    "Black", 
    mom_race_eth
  ))

# 3. Now lets filter to just year 2017! We'll make a new dataframe for plotting
# so that we can preserve the other years of data, too! 
fetal_data_plot <- fetal_data_new %>% filter(year == 2017)

# 4. Plot! 
ggplot(fetal_data_plot, aes(
    x = fetal_deaths,
    y = reorder(state, total_fetal_deaths),
    color = mom_race_eth_plot
  )) +
  geom_point() +
  theme_minimal() +
  ylab("") + xlab("Fetal deaths, N") +
  scale_color_brewer("Mom race/ethnicity", palette = "Set1")

```

This sort of looks like a plot of total population, we need denominators. Let's use live births as a denominator. 

### IV. Pull in live birth data to use as a denominator, clean, replot!
We will use CDC wonder live births data. This is already in the repo, but you can find it here if you are interested: https://wonder.cdc.gov/natality.html
```{r outcome_plot_denom, echo=TRUE, warning=FALSE}
# Let's bring in live births as our denominator. 
births <- read_csv(here("data/lab/01/births.csv")) 
glimpse(births)

# Do we have NAs? 
table(births$mom_race_eth, useNA = "always")
table(births$year, useNA="always")
table(births$state_code, useNA="always")

# Let's drop all NAs since we don't need them for this analysis. This will 
# drop NAs across all variables in our dataframe `births` and then
# we can double check it. 
births <- drop_na(births)
table(births$mom_race_eth, useNA = "always")
table(births$year, useNA="always")
table(births$state_code, useNA="always")

# OK, now let's add total live birth counts to use as the denominator for our 
# fetal deaths plot above. 
fetal_data_complete <- left_join(fetal_data_new,
                            births, 
                            by = c("state" = "state", 
                                   "mom_race_eth" = "mom_race_eth", 
                                   "year" = "year", 
                                   "state_code" = "state_code"))
head(fetal_data_complete)

# Create variable scaling fetal deaths by total life births and changing it
# to be per 1,000 live births.
fetal_data_complete <- fetal_data_complete %>% 
  mutate(fetal_death_scaled = fetal_deaths/births*1000)

# Now let's visualize prevalence for 2017 again! 
fetal_data_plot2 <- fetal_data_complete %>% filter(year == 2017) 

ggplot(fetal_data_plot2,
       aes(x = fetal_death_scaled, 
           y = reorder(state, fetal_death_scaled), 
           color = mom_race_eth)) + 
  geom_point() +
  theme_minimal() +
  ylab("") + 
  xlab("Fetal deaths per 1000 live births, N") +
  scale_color_brewer("Mom race/ethnicity", palette = "Set1")

```

Much more informative, but what's happening with states with only white rate?


## Part 2: Mapping 
Let's take a look at the states using a map, which may be easier to interpret! 


### I. Read in US states shapefile and join to outcome data 
```{r prep_outcome_map, echo=TRUE, warning=FALSE}
# Reading in a shapefile using st_read
states <- st_read(here("data/lab/01/US_State_Albers.shp"))
head(states) 
```

In order to map things, we use data with a CRS. What is the CRS? A CRS is a coordinate reference system and allows us to geolocate places on Earth using coordinates. You must be careful about CRS when working with spatial data! Read more about CRS [here](https://datacarpentry.github.io/organization-geospatial/03-crs.html) and about CRS in R [here](https://rspatial.org/spatial/6-crs.html)

For this project, we will use a projected CRS calledNorth America Albers Equal Area Conic. You can read more [here](http://www.geo.hunter.cuny.edu/~jochen/gtech201/lectures/lec6concepts/Map%20coordinate%20systems/Albers%20Equal%20Area%20Conic.htm)   

```{r outcome_map, echo=TRUE, warning=FALSE}
st_crs(states)

# Add the fetal death data to the spatial file by state name (note these are 
# different variable names in each dataset)
fetal_spatial <- left_join(states, fetal_data_complete, by = c("STATE_NAME" = "state"))
glimpse(fetal_spatial)
```

### II. Make some maps using continuous fetal deaths

For our first map, let's just subset to 2017 and plot: 
```{r outcome_map1, echo=TRUE, warning=FALSE, out.width="150%"}
fetal_plot3 <- fetal_spatial %>% filter(year == 2017)

ggplot(fetal_plot3) +
  geom_sf(aes(fill = fetal_death_scaled),
          color = "white",
          lwd = 0.1) +
  scale_fill_viridis_c("Fetal deaths", na.value = "grey") +
  facet_wrap( ~ mom_race_eth_plot) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  theme(panel.grid.major = element_blank(),
        # Hide panel borders and remove grid lines
        panel.grid.minor = element_blank()) +
  theme(legend.position = "bottom", legend.box = "horizontal")

```

Let's try looking at all years. We can map the number of fetal deaths per 1000 live births by race/ethnicity. To plot all years, we can use `facet_grid` and see each year clearly. To read more about this, type `?facet_grid` into your console.

```{r outcome_map2, echo=TRUE, warning=FALSE, out.width="150%"}
fetal_plot4 <- fetal_spatial # just doing this for consistency 

ggplot(fetal_plot4) +
  geom_sf(aes(fill = fetal_death_scaled),
          color = "white",
          lwd = 0.1) +
  scale_fill_viridis_c("Fetal deaths per 1000 live births", na.value = "grey") +
  theme_minimal(base_size = 14) +
  facet_grid(mom_race_eth_plot ~ year) + 
  # Does using facet_grid make sense here? Seems no to me as you can't see the 
  # variability in white fetal death
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(legend.position = "bottom", legend.box = "horizontal")
```

The continuous scale is making it a little harder to see what is happening. Let's create quintiles for the legend to make it a bit easier! 

### III. Reshape data to map quintiles for interpretability 

```{r outcome_map3, echo=TRUE, warning=FALSE}
# Let's create quintiles for the legend
qnt <- quantile(fetal_spatial$fetal_death_scaled, c(.2, .4, .6, .8), na.rm = T)
 # take a look at quintiles. we can pull out the values using double brackets. 
 # try running this to see what it gives you: 
 qnt
 qnt[[1]]
 qnt[["20%"]]
 # these are the same so we could use either one! 
 
# Now let's use this to create our quintile variable! 
fetal_spatial <- fetal_spatial %>%
  mutate(
    fetal_death_q = case_when(
      fetal_death_scaled < qnt[[1]] ~ 1,
      fetal_death_scaled >= qnt[[1]] &
        fetal_death_scaled < qnt[[2]] ~ 2,
      fetal_death_scaled >= qnt[[2]] &
        fetal_death_scaled < qnt[[3]] ~ 3,
      fetal_death_scaled >= qnt[[3]] &
        fetal_death_scaled < qnt[[4]] ~ 4,
      fetal_death_scaled >= qnt[[4]] ~ 5
    )
  )
qnt_labs <- c(paste('<', round(qnt[[1]], 2)),
              paste0('[', round(qnt[[1]], 2), '-', round(qnt[[2]], 2), ')'),
              paste0('[', round(qnt[[2]], 2), '-', round(qnt[[3]], 2), ')'),
              paste0('[', round(qnt[[3]], 2), '-', round(qnt[[4]], 2), ')'),
              paste('\u2265', round(qnt[[4]], 2)))
# alternate method: 
# qnt_labs <- c(paste('<', round(qnt[['20%']], 2)),
#               paste0('[', round(qnt[['20%']], 2), '-', round(qnt[['40%']], 2), ')'),
#               paste0('[', round(qnt[['40%']], 2), '-', round(qnt[['60%']], 2), ')'),
#               paste0('[', round(qnt[['60%']], 2), '-', round(qnt[['80%']], 2), ')'),
#               paste('\u2265', round(qnt[['80%']], 2)))


qnt_labs
```

```{r quintiles2, echo=TRUE, warning=FALSE, out.width="150%"}
### Alternate method of creating this variable... as a factor with cut()
### No need for case_when() and makes scale_fill_viridis() simpler to use ...
# Note that you need 0 and infinity included as breaks here, whereas you didn't 
# need those above! That shifts the numeric indexing of `qnt_alt` to be 
# different from that of `qnt`! 
# qnt_alt <- c(0, quantile(fetal_spatial$fetal_death_scaled, c(.2, .4, .6, .8), na.rm = T), Inf)
# qnt_labs_alt <- c(paste('<', round(qnt_alt[[2]], 2)),
#               paste0('[', round(qnt_alt[[2]], 2), '-', round(qnt_alt[[3]], 2), ')'),
#               paste0('[', round(qnt_alt[[3]], 2), '-', round(qnt_alt[[4]], 2), ')'),
#               paste0('[', round(qnt_alt[[4]], 2), '-', round(qnt_alt[[5]], 2), ')'),
#               paste('\u2265', round(qnt_alt[[5]], 2)))
# fetal_spatial <-
#   fetal_spatial %>% mutate(
#     fetal_death_q_fctr = cut(
#       x = fetal_death_scaled,
#       breaks = qnt_alt,
#       labels = qnt_labs_alt,
#       right = FALSE,
#       include.lowest = TRUE,
#       ordered = TRUE
#     )
#   )

# Now lets plot our quintiles! 
fetal_plot5 <- fetal_spatial

ggplot(fetal_plot5) +
  geom_sf(aes(fill = factor(fetal_death_q)),
          color = "white",
          lwd = 0.1) +
  scale_fill_viridis(
    "Fetal deaths",
    na.value = "grey",
    discrete = T,
    breaks = c(1, 2, 3, 4, 5),
    labels = qnt_labs
  ) +
  theme_minimal(base_size = 14) +
  facet_grid(mom_race_eth_plot ~ year) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(legend.position = "bottom",
        legend.box = "horizontal")

```


This is the end of class. If you wish to explore cartograms and regression, see below! 

## Part 3 (OPTIONAL): Cartograms
```{r cartograms, echo=TRUE, warning=FALSE, results='hide', message=FALSE}
# Cartograms
st_crs(fetal_spatial)
# Look up what this projection is at spatialreference.org
fetal_spatial <- st_transform(fetal_spatial, 2163)
st_crs(fetal_spatial)

# Create cartogram for Black and white fetal deaths in 2017
fetal_spatial_black <- fetal_spatial %>% 
  filter(mom_race_eth == "Black or African American" & year == 2017)
fetal_spatial_white <- fetal_spatial %>% 
  filter(mom_race_eth == "White" & year == 2017) 

fetal_spatial_fetaldeath <- cartogram_cont(fetal_spatial_black, "fetal_death_scaled", 
                                    itermax = 10, 
                                    threshold = .1)
fetal_spatial_fetaldeath2 <- cartogram_cont(fetal_spatial_white, 
                                     "fetal_death_scaled", 
                                     itermax = 10, 
                                     threshold = .1)

# Plot the cartograms
tm_shape(fetal_spatial_fetaldeath) + 
  tm_polygons("fetal_death_scaled", style = "jenks") +
  tm_layout(frame = FALSE, legend.outside = TRUE)

tm_shape(fetal_spatial_fetaldeath2) + 
  tm_polygons("fetal_death_scaled", style = "jenks") +
  tm_layout(frame = FALSE, legend.outside = TRUE)

```


## Part 4 (OPTIONAL): Regression
In this part, we will add in information on smoking. These data are in the repo already, but you can find the data we are using, which are cigarette smoking data from the EH Tracking Network, here: https://www.cdc.gov/nceh/tracking/topics/LifestyleRiskFactors.htm

### I. Add in smoking data for analysis 
```{r smoke, echo=FALSE, warning=TRUE, message=FALSE}
cig <- read_csv(here("data/lab/01/cig_repro_age_state.csv"))
glimpse(cig)

# Want overall average by state and year in the 18-44 age group
cig <- cig %>% 
  group_by(state, year) %>%
  dplyr::summarise(prop_smokers = mean(proportion_smok, na.rm = T))
summary(cig$prop_smokers) # ranges from 9.3% to 33.7%

fetal_data_cigs <- left_join(fetal_data_complete, cig, 
                            by = c("state" = "state", "year" = "year"))

# Correlation between smoking and fetal deaths
fetal_data_cigs %>% 
  select(prop_smokers, fetal_death_scaled) %>% 
  correlate() 

# Add cigarette smoking to states
states <- st_read(here("data/lab/01/US_State_Albers.shp"))
head(states)

# Add fetal death data to states shapefile
fetal_data_cigs_spatial <- left_join(states, fetal_data_cigs, by = c("STATE_NAME" = "state"))

# Change prop to percent
fetal_data_cigs_spatial <- fetal_data_cigs_spatial %>% mutate(percent_smokers = prop_smokers*100)

head(fetal_data_cigs_spatial)

```

### II. Poisson regression
Now we can try to run some simple regression models. Let's start with linear regression: 
```{r linear_reg, echo=TRUE, warning=FALSE, message=FALSE}
# Basic poisson model
# Check distribution of fetal_deaths
fetal_data_cigs_spatial %>% ggplot(aes(y=fetal_deaths)) + geom_histogram()

smoke_poisson <- glm(fetal_deaths ~ percent_smokers + factor(year) + 
                       factor(mom_race_eth) + offset(log(births)), 
                     data = fetal_data_cigs_spatial, family = poisson(link = "log"))
summary(smoke_poisson)

# pull out and exponentiate coefficient 
coefficient <- coef(smoke_poisson)[["percent_smokers"]]
exp(coefficient)

# Is there spatial autocorrelation in the data that we need to account for?
# Let's look at the residuals of our regression model
fetal_data_nomiss <- fetal_data_cigs_spatial %>% 
  drop_na(percent_smokers, fetal_deaths, births, mom_race_eth)
fetal_data_nomiss$residuals <- smoke_poisson$residuals
fetal_data_nomiss <- fetal_data_nomiss %>% 
  select(year, STATE_NAME, mom_race_eth, residuals, mom_race_eth)
```

### III. Plotting and model diagnostics 
```{r poisson_diagnostics, echo=TRUE, warning=FALSE}
# Is there spatial autocorrelation in the data that we need to account for?
# Let's look at the residuals of our regression model
fetal_data_nomiss <- fetal_data_cigs_spatial %>% 
  drop_na(percent_smokers, fetal_deaths, births, mom_race_eth)
fetal_data_nomiss$residuals <- smoke_poisson$residuals
fetal_data_nomiss <- fetal_data_nomiss %>% 
  select(year, STATE_NAME, mom_race_eth, residuals, mom_race_eth)


# Do we see a spatial pattern in the residuals?
ggplot(fetal_data_nomiss) +
  geom_sf(aes(fill = residuals),
          color = "white",
          lwd = 0.1) +
  scale_fill_viridis("Residuals",
                     na.value = "grey",
                     option = "A") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    rect = element_blank()
  ) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(legend.position = "bottom", legend.box = "horizontal")
```

Does it look random?

```{r diagnostics2, echo=TRUE, warning=FALSE}

# Create a neighbor matrix, queen matrix identifying queen-type neighbors
nb <- poly2nb(fetal_data_cigs_spatial, queen = TRUE)

# Assigning weights 
lw <- nb2listw(nb, style = "S", zero.policy = TRUE)

# First polygon's weights,
lw$weights[1]

# Get Moran's I
set.seed(111)
MC <- moran.mc(fetal_data_cigs_spatial$fetal_death_scaled, lw, na.action = na.exclude, nsim = 500)
MC

```
We reject the hypothesis that there is no global spatial autocorrelation here. 

